Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-22 ms.tex
some progress on compact source subsection, still needs major work

\subsection{Compact Sources}
\label{sec:ptsrc}
To mask compact sources, we use the SFD compact source mask, which was 
originally constructed to mask point sources and resolved compact objects
that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked. We have inspected all of 
the maps used in this analysis and do not see any evidence that this compact 
source mask fails to adequately mask compact sources in the \PLANCK~data. In 
practice, we perform our dust SED fits in all pixels, even those flagged by 
the point source mask. Compact source affected pixels can be ignored or 
interpolated over downstream.
%maybe say that we're releasing a version of the map with point sources
%interpolated over by us as well

>>>>

\subsection{Compact Sources}
\label{sec:ptsrc}
%start by mentioning that SFD removed compact sources (outside of b +/- 5)
After subtracting the \verb|SMICA| CMB model, we next proceeded to interpolate 
over compact sources, including both point sources and resolved galaxies. 
Removing compact sources at this stage is important as it prevents 
contamination of compact-source-free pixels in our downstream analyses which 
require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
galaxies from the \verb|i100| map everywhere outside of 
$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
\verb|i100| map to account for compact sources. To mask compact sources in the 
\PLANCK~maps, we use the SFD compact source mask, which was originally 
constructed to mask point sources and resolved compact objects that are not 
part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
$\S$\ref{sec:pix}), 1.56\% of pixels are masked.

%this compact source section still needs a lot of work

% probably best to refer to an appendix for details of the point source
% masking
